\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/implementation.tex

For example, the \textit{ReverseShell} program is 355 SPASM instructions, and
makes six system calls to open a socket,
connect to it, duplicate I/O file descriptors, and perform an \texttt{execve}
system call to open a shell.
In our tests using 256 iterations per decrypted instruction, the
\textit{ReverseShell} program takes under 7 seconds to launch a reverse shell
once triggered.

>>>>

For example, the \textit{ReverseShell} program is 355 SPASM instructions, and
makes six system calls to open a socket,
connect to it, duplicate I/O file descriptors, and perform an \texttt{execve}
system call to open a shell.
In our tests using 5 iterations per decrypted instruction, the
\textit{ReverseShell} program takes just over 2ms to launch a reverse shell
once triggered.
